Deliminative verbal reduplication in Mandarin Chinese

### 2025-11-11 chapters/ch02-Phenomenon.tex
modify reviewer replies and modify paper accordingly
last changes replaced English tense inflection by German adjective inflection

\ea\label{ex:rel1}
% 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
\gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\footnotemark\\
you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} several-ten \textsc{clf} Weibo\\ \jambox{(BCC)}
\glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'

% 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）

@@

\z  
\z
\footnotetext[]{We found this sentence in the BCC corpus, but one reviewer finds it unnatural.
    We asked 10 native speakers from different regions in Mainland China. 
    All found the sentence weird at first glace, but considered that the acceptability can be greatly improved 
    by adding more information to support the use of reduplication, such as \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{zheng4wu4wei1bo2} `the government affairs Weibo account that you look at \textit{casually}'.
    Three of them further insist on the use of a demonstrative: \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{na4} \obj{ge4} \obj{zheng4wu4wei1bo2} `\textit{that} government affairs Weibo account that you look at \textit{casually}'.
    These still constitute cases where reduplication occurs in relative clauses without modal or mood verbs 
    and thus strengthen our claim.}

@@

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \obj{-able} derivation in English is a productive morphological process.
Tense inflections in English such as \obj{-ed} change neither the category nor the valency of the input verb.\footnote{
We do not claim reduplication to be either inflection or derivation.
}
%the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
%The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
%And inflections of tense in German do not change the valency of the input verb.
Further, if \obj{le} is considered to be a morphological element (e.g.\ \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only shows that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.

>>>>

\ea\label{ex:rel1}
% 你看看的政务 微博2010年9月2号、10月20号和10月21号，应付转发了几十条微博！（BCC 微博）
\gll [[\objex{ni3} \obj{kan4-kan} \objex{de}] \objex{zheng4wu4}-\objex{wei1bo2}] \ldots\, \objex{zhuan3fa1-le} \objex{ji3}-\objex{shi2} \objex{tiao2} \objex{wei1bo2}!\footnotemark\\
you look-look \textsc{de} government.affairs-Weibo {} repost-\textsc{pfv} several-ten \textsc{clf} Weibo\\ \jambox{(BCC)}
\glt `The government affairs Weibo account that you look at \ldots\, reposted dozens of Weibo posts.'
\footnotetext{We found this sentence in the BCC corpus, but one reviewer finds it unnatural.
    We asked 10 native speakers from different regions in Mainland China. 
    All found the sentence weird at first glace, but considered that the acceptability can be greatly improved 
    by adding more information to support the use of reduplication, such as \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{zheng4wu4wei1bo2} `the government affairs Weibo account that you look at \textit{casually}'.
    Three of them further insist on the use of a demonstrative: \obj{ni3} \obj{sui2bian4} \obj{kan4kan} \obj{de} \obj{na4} \obj{ge4} \obj{zheng4wu4wei1bo2} `\textit{that} government affairs Weibo account that you look at \textit{casually}'.
    These still constitute cases where reduplication occurs in relative clauses without modal or mood verbs 
    and thus strengthen our claim.}
% 大年初一参差光谷，初二去，初三去看看的店 （BCC 微博）

@@

@@

However, a morphological process can be productive, and it does not necessarily change the part of
speech label or valency of the input. For instance, the \obj{-able} derivation in English is a productive morphological process.
The adjective inflection in languages like German does change neither the part of speech nor the
valency of the adjectival stem.\footnote{
We do not claim reduplication to be either inflection or derivation.
}
% $^,$\footnote{A reviewer pointed out that tense inflection is assumed to live under the category T or
%   Infl in theories within the framework of Government \& Binding \citep{Chomsky81a}. HPSG follows
%   the lexicalist view according to which single morphemes are not syntactic objects. See
%   Müller (\citeyear{MuellerGermanic}, \citeyear{MuellerLFGTAG}) on functional projections. 
% }
%the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
%The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
%And inflections of tense in German do not change the valency of the input verb.
Further, if \obj{le} is considered to be a morphological element (e.g.\ \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \obj{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only shows that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.
